%%

\cvsection{About Me}

\begin{flushleft}
\justifying
I am a driven, self-motivated student, looking to expand my horizons by learning to build
software the right way, as part of a bigger team. I am self-sufficient and thrive in ambiguity.

\end{flushleft}

\cvsection{Notable Skills}

\small
\cvtag{Java}
\cvtag{Spring}
\cvtag{Spring Data}
\cvtag{Spring Web}
\cvtag{JavaScript}
\cvtag{Bash}
\cvtag{SQL}
\cvtag{Docker}
\cvtag{Firecracker}
\cvtag{Virtualization}
\cvtag{Linux}

\cvsection{Featured Projects}

\begin{itemize}
    \item \justifying \href{https://github.com/zsadeghi/benchpress}{\githubsymbol \textbf{/benchpress} \externalLink} Capstone project with full grade
    (4.0) under the supervision of \href{http://faculty.washington.edu/wlloyd/}{Dr. Wes. J. Lloyd}. \\
    \faEye{} Ongoing project, under a private repository. Access and metrics can be shared upon request.
    \item \justifying \href{https://github.com/zsadeghi/pandora}{\githubsymbol \textbf{/pandora} \externalLink} Extensible distributed key-value supporting replication, multiple protocols, as well as Raft. 
    \item \justifying \href{https://github.com/zsadeghi/starbox}{\githubsymbol \textbf{/starbox} \externalLink} Web-based application for managing the websites of a chain of coffeeshops.
    \item \justifying \href{https://github.com/zsadeghi/grizzle}{\githubsymbol \textbf{/grizzle} \externalLink} A semantic search engine for \href{http://millionsongdataset.com/}{the million song dataset}.
\end{itemize}

\cvsection{Publications}

\begin{itemize}
    \item \href{https://dx.doi.org/10.1063/1.4823715}{The modified equation for spinless particles and superalgebr, Journal of Mathematical Physics, 2013 \externalLink}
    \item \href{https://link.springer.com/article/10.1007/s10773-013-1542-2#page-1}{Thermodynamics of Near-Extremal Solutions of Einstein-Maxwell-Scalar Theory, Springer, 2013 \externalLink}
    \item \href{http://faculty.washington.edu/wlloyd/papers/cbdcom_FaaSProgrammingLanguagePaper_camera_ready.pdf}{Cordingly, R., Yu, H., Hoang, V., Perez, D., Foster, D., Sadeghi, Z., Hatchett, R., Lloyd, W., Implications of Programming Language Selection for Serverless Data Processing Pipelines, 2020 6th IEEE International Conference on Cloud and Big Data Computing (CBDCOM 2020), Aug 17-24, 2020}
\end{itemize}

\cvsection{Featured Courses}

Courses with distinguished grades.

\small
\cvtag{Distributed Systems}
\cvtag{Information Theory}
\cvtag{Research: Virtualization}
\cvtag{Capstone Project}

\cvsection{Languages}

\cvskill{English}{5}
\cvskill{Persian}{5}
